Computer Science House Constitution

### 2015-12-17 articles.tex
Update articles.tex

	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Balloted Vote}.
	\item The winners are determined by a simple majority vote of the ballots cast as defined in 5.C.1, Voting. A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official. All winners are notified of their election. If the position is currently vacant, the winner immediately assumes office. If not, the winner will assume office at the end of the current term (\ref{Term}). Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Types of Voting}
\asubsection{Alternative Vote}
\asubsubsection{Method of Vote}
Each voter has one vote, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.

>>>>

	\item At the end of the voting period, the Chairman will terminate voting by collecting the ballot box and the votes shall be counted as stated in \ref{Alternative Vote}.
	\item The winners are determined via the process described in \ref{Alternative Vote}. A quorum of fifty-percent of the number of all members eligible to vote is required for the election to be official. All winners are notified of their election. If the position is currently vacant, the winner immediately assumes office. If not, the winner will assume office at the end of the current term (\ref{Term}). Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Types of Voting}
\asubsection{Alternative Vote}
\asubsubsection{Method of Vote}
Each voter has one vote, given to them in the form of a paper ballot, but rather than an X, they put a '1' by their first choice a '2' by their second choice, and so on, until they no longer wish to express any further preferences or run out of candidates.
